---
title: "Hw1GoogleAnalytics"
author: "Bryan Tamsir, Erik Chu, Hariz Mohd Rani Hisham, Yi-Yun Su"
date: "1/22/2019"
output: html_document
---

```{r Setup}
#Set WD 
rm(list = ls()) #to clear global environment
library(data.table)
```

```{r Upload Data Manually and set a key}
dtsum = fread("~/Documents/Academic/MA/hw1/GoogleMerchandise2016_2017_summary.csv")
dthits = fread("~/Documents/Academic/MA/hw1/GoogleMerchandise2016_2017_Hits.csv")

```

### Question 1

1. What share of visits with products added to cart end in a purchase?

We set the keys as fullVisitorId, visitId, and hitNumber
We subsetted the hits data for action types 3 and 6
Merge both data tables and grouped by fVId and vId

```{r q1}
# Create new Data Table
uniqueN(dthits[, .(fullVisitorId, visitId, hitNumber)] ) / dthits[,.N]
setkey(dthits, fullVisitorId, visitId, hitNumber)

table(dthits$action_type)
#67 # for actiontype 3
#24484 for actiontype 6

#Subset into appropriate data table and set the key for each. 
purchase = dthits[action_type==6, .(fullVisitorId, visitId, action_type) ]
addtocart = dthits[action_type==3, .(fullVisitorId, visitId, action_type) ]
checkout = dthits[action_type==5, .(fullVisitorId, visitId, action_type) ]

#Set keys for all data tables
setkey(purchase, fullVisitorId, visitId, action_type)
setkey(addtocart, fullVisitorId, visitId, action_type)
setkey(checkout, fullVisitorId, visitId, action_type)

final = merge(addtocart, purchase, by=c("fullVisitorId", "visitId"), all.x = TRUE)
onea = sum(final$action_type.y == 6, na.rm = T) / sum(final$action_type.x == 3) #for some reason the first half does not work
onea
#answer is 5.797%
```
```{r q1: course discussion}
shr = dthits[,.(numAdd = sum(action_type == 3, na.rm = T), numPur = sum(action_type == 6, na.rm = T)),.(fullVisitorId, visitId)]
onea = sum(shr$numPur > 0, na.rm = T) / sum(shr$numAdd > 0) 
onea
```
### Question 1b

1b. What share of visits with a "Check out\"" end in a purchase?

``` {r q1b}
finalb = merge(checkout, purchase, by=c("fullVisitorId", "visitId"), all.x = TRUE, allow.cartesian=TRUE)
oneb = sum(finalb[!is.na(action_type.y), .N]) / sum(finalb$action_type.x == 5)
oneb
# answer is 84%
```
### Question 2

What is the distribution of time from the start of a session to when a purchase is made? Plot hist, mean, min, max, median.

Subset on action type 6 (purchases) from hits table
Set keys
Divided time by 60000 to convert ms to minutes
View histogram 

``` {r q2}
time1 = dthits[action_type == 6, .(fullVisitorId, visitId, action_type, time, hitNumber) ]
setkey(time1, fullVisitorId, visitId, hitNumber)
hist( 
  time1$time / 60000, 
  breaks=50,
  main="Time between the start of a session and a Purchase", xlab="minutes")
summary(time1$time / 60000) #in minutes

```
### Question 3

Q3 - What is the distribution of time from “Check out” to “purchase made”? Plot the histogram and report the min, max, mean and median.

```{r q3}
purchase3 = dthits[action_type == 6, .(fullVisitorId, visitId, action_type, time) ]

dthits[action_type == 5, time1 := min(time), .(fullVisitorId, visitId)]
checkout3 = dthits[action_type==5, .(fullVisitorId, visitId, action_type, time1) ]

setkey(purchase3, fullVisitorId, visitId)
setkey(checkout3, fullVisitorId, visitId)

temp = merge(checkout3, purchase3, 
                  by = c("fullVisitorId", "visitId"), 
                  all.x = TRUE,
                  allow.cartesian = TRUE)
question3 = temp[complete.cases(temp), ]
question3[ , timeDiff := ifelse((time - time1) > 0, time- time1, NA)]
question3$timeDiff = question3$timeDiff / 60000

hist( 
  question3[, timeDiff], 
  breaks = 50,
  main = "Time between checkout and purchase", xlab = "Time in minutes")
summary(question3$timeDiff)
```
### Question 4

What are the bounce rates for the ten largest landing pages (largest by number of visits.)
(Hint: this will require you to merge the "Hits" and "Summary" data sets. See the document "data.table-Keys-andMerge.Rmd" for help.)

Merge hits with summary on fVId and vId 
Calculated number of obs for each unique landing screen name 
Calculated bounces rates for each unique landing screen name
Output: List of landing screen names, bounce rate associated, no. of obs.

``` {r q4}
hits_4 <- merge(dtsum, 
                dthits[, .(fullVisitorId, visitId, hitNumber, landingScreenName)], 
                by = c("fullVisitorId", "visitId")) 

hits_4[, .(bouncerate = sum(bounces, na.rm = T) / .N, N_obs = .N), 
       landingScreenName][order(-N_obs)][1:10]

```